---
title: "DAS data first look"
author: "Rhian Davies"
date: "15 February 2017"
output: html_document
---

```{r setup, include=FALSE}
#read in libraries
library("ggplot2")
library("dplyr")
library("reshape")
```

## R Markdown

* The sample Rebecca sent to me is 100,000 x 790.
* The data is thinned, we have every 10th timepoint. 
* My initial work just looks at first 10,000 data points

```{r read_in_data}
x = read.csv("data/minisample.csv", header = T, stringsAsFactors = F)
```

## The features

* There are 790 features each corresponding to an acoustic sensors?
* Earlier ones may have more information? Any application knowledge Idris?

```{r bunch_o_figs, fig.height=3, fig.width=14, echo = FALSE}
par(mfrow=c(1,2), las=1)
for(i in c(1,2,3,4,5,6,50, 75,100,200,400,700)) {
  plot(1:nrow(x), x[,i], main=i, type = "l")
}
```


# Clustering raw data using just first 6 features (raw, no pca)

* First we try simple offline k-means
```{r offline_kmeans, fig.height=4, fig.width=14, echo = FALSE}
off_k = kmeans(x[,1:6],7 )
par(mfrow=c(1,2), las=1)
for(i in c(1:6)) {
  plot(1:nrow(x), x[,i], main=i, type = "p", col = off_k$cluster)
}
```

The size of the clusters are `r off_k$size`. 


# PCA 

```{r pca_plots, fig.height=4, fig.width=14, echo = FALSE}
pca <- prcomp(x, center = TRUE, scale = TRUE) 
plot(pca)


off_k_pca = kmeans(pca$x[,1:6], 7 )
par(mfrow=c(1,2), las=1)
for(i in c(1:6)) {
  plot(1:nrow(pca$x), pca$x[,i], main=i, type = "p", col = off_k_pca$cluster)
}

```

* Kmeans using just first 6 principle components
* 7 clusters

